Think deep for reef resilience

### 2025-07-15 paper/paper_draft.qmd
Soften/qualify language

Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response
research enable integrated investigation of how these multiple factors interact to determine
climate resilience. By incorporating the latest coral population models
[@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections
[@dixon2022], we can examine which factors most strongly influence reef persistence under
different scenarios. While connectivity has been emphasized as critical for GBR resilience
[@hock2017], our integrated modelling reveals that environmental factors - particularly
depth - may play a more fundamental role in determining which reefs maintain viable coral
populations and positive carbonate budgets under projected climate conditions.

>>>>

Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response
research enable integrated investigation of how these multiple factors interact to determine
climate resilience. By incorporating the latest coral population models
[@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections
[@dixon2022], we can examine which factors most strongly influence reef persistence under
different scenarios. While connectivity has been emphasized as critical for GBR resilience
[@hock2017], and remains an important consideration, our integrated modelling reveals depth
may play a fundamental role in determining maintenance of reef coral population and positive
carbonate budgets under current projections of climate change.
